\def\handout{0}   % set to 1 to produce 4-up handouts instead of slides
\def\notes{0}     % set to 1 to show \note{}s
\def\adminstuff{0}
\input{lec_customize}
%\input{customize}
\date{}
\usepackage{hyperref}
\begin{document}

\begin{frame}
\title{Introduction to Development}
\author{Aman Agrawal}
\institute{aman.cs115@cse.iitd.ernet.in}
\titlepage
\end{frame}

\section{About Us}
    \begin{frame}{About Us}
        \uncover<+->{Here is what our website says:\\}
        \uncover<+->{
        \begin{quote}
            Dev Club is a student group that tries to innovate and foster technical activities, and create a coding culture which is somewhat missing.             
        \end{quote}
        }
        \uncover<+->{We develop cool stuff that benefits everyone in the campus.\\}
        \uncover<+->{Like:\\}
        \begin{itemize}
            \item<+-> \href{https://aman71197.github.io/CampusBot/}{Campus Bot}
            \item<+-> \href{http://iitd.info/study_portal}{Study Portal}            
            \item<+-> \href{http://10.17.51.99:3000/}{Multiplayer Game}
            \item<+-> \href{http://sendata.herokuapp.com/}{SenData}
            \item<+-> \href{http://www.cse.iitd.ernet.in/devclub/}{Our own Website}
        \end{itemize}
    \end{frame}

\section{Introduction}
    \begin{frame}{What is Software Development?}
        \uncover<+->{Here is what wikipedia says:\\}
        \uncover<+->{
        \begin{quote}
            Software development is the process of computer programming, documenting, testing, and bug fixing involved in creating and maintaining applications and frameworks resulting in a software product.
        \end{quote}
        }
        \uncover<+->{Why is it useful?\\}
        \begin{itemize}
            \item<+-> You will become a better, more efficient, and less error-prone coder.
            \item<+-> Necessary for a lot of coding jobs and something that is NOT taught in college            
            \item<+-> You win prizes and trips to places around the world as you compete with and meet other motivated and smart students.
        \end{itemize}
    \end{frame}
    \begin{frame}{Pre-requisites}
        Here are some pre requisites:
        \pause
        \begin{itemize}
            \item<+-> Language basic of either C++, Java or Python.
            \item<+-> Ability to read documentations effeciently.
            \item<+-> Able to do a good GOOGLE Search !!            
            \item<+->[] \textit{And most importantly,}
            \item<+-> Perseverance
        \end{itemize}
    \end{frame}

\section{Learning Stuff}
    \begin{frame}{What Can we learn?}
        \begin{itemize}
            \item<+-> Making \textbf{best UI/UX} using angular, react, bootstrap, etc.
            \item<+-> \textbf{Server side management} : Docker, Resource management, Sandboxing, Monitoring, etc.
            \item<+-> \textbf{Back end} : Node.js, Django, Rust, Scala, Julia....
            \item<+-> \textbf{Tools} : Git, Slack, IRC, Database (SQL, NoSQL ..)..
            \item<+-> And a hell lot which even we don’t know that we don’t know
        \end{itemize}
    \end{frame}


\end{document}

